Fourmile Calibrations and Output

### 2024-07-17 fourmile_outputs_2013edits.Rmd
dont need all RD RG cals in there

<!-- # -->
<!-- params_weighted1 <- params_weighted %>% -->
<!--   rename(input_data = cal) %>% -->
<!--   pivot_wider(names_from = 'param', -->
<!--               values_from = 'area_weighted_average') %>% -->
<!--   rename_with(~ paste0(., '_weighted'), 2:7) -->

@@

<!-- write_csv(join, 'flow_params.csv') -->

>>>>

<!-- # -->
<!-- params_weighted1 <- params_weighted %>% -->
<!--   mutate(input_data = paste(source, year_missing, sep = "_")) %>%  -->
<!--   pivot_wider(names_from = 'param', -->
<!--               values_from = 'area_weighted_average') %>% -->
<!--   rename_with(~ paste0(., '_weighted'), 4:9) %>% -->
<!--   dplyr::select(-c(year_missing, source)) -->

@@

<!-- write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv') -->
